---
title: "Classwork Activity"
author: "Camila Hernandez"
output:
  html_document:
    df_print: paged
---


# Instructions (Step by Step)

## Step 1: Create fake data
```{r}
# Creating a small fake dataset
set.seed(2073) # allows for reproducibility 

students <- data.frame(
  Name = paste("Student", 1:20),
  StudyHours = round(runif(20, 1, 10), 1),
  Satisfaction = round(rnorm(20, mean = 7, sd = 1.5), 1),
  Major = sample(c("Data Science", "Business Analytics", "Math", "Computer Science"), 20, replace = TRUE)
)

head(students)
```

## Step 2: Drop a column

```{r}
library(dplyr)
```

```{r}
# Remove the Name column
Students_Clean <- students %>%
  select(-Name)


Students_Clean
```


### Question:
Why might someone drop a column like name or ID from a dataset?
- Someone might drop a column like name or ID from a dataset because a analysis of data from other columns might be needed, where names or ids aren't really  relevant. An example, an analysis focuses on trends by majors rather than individual students. 

### Answer:

## Step 3: Visualize
```{r}
library(ggplot2)
```

```{r}
ggplot(Students_Clean, aes(x = Major, y = Satisfaction, fill = Major)) +
  geom_boxplot() +
  labs(
    title = "Student Satisfaction by Major",
    x = "Major",
    y = "Satisfaction (1–10)"
  ) +
  theme_minimal()
```


## Step 4: Explain: Write 2–3 sentences each

### Questions:

1. What pattern or difference do you see in the chart?
-  Math has the smallest amount of students yet, is the highest in satisfaction. There isnt really a claer pattern or relation between the number of students and  the satisfaction. 

2. What might explain it?
- This could be because of many different reasons, class sizes, professors, students preferences and many other factors

3. Do you think this chart is accurate?
- It could be but definitely not the most accurate.

4. Why? Why not?
- This is a very small amount of student surveyed, there aren't equal amounts of data from students in each major so the data might not represent the whole groups opinion, especially a whole major.

## Step 5: Questions on Git, GitHub and R Markdown

### Questions:

1. What does git add do?
2. What is the difference between git commit and git push?
3. Why is it useful to use GitHub for your code or data projects?
4. How could version control help when collaborating?
5. What is the difference between a code chunk and regular text in R Markdown?
6. How could R Markdown help you explain your analysis to someone else?

### Answers:
1. Add files to a commit
2. Git commit saves it in your computer and git push updates the files in git hub
3. It stores all your code in one place and makes it easily accessible
4. This shows the changes made so people collaborating don't overwrite other peoples code and it lets you see all past changed made.
5. A code chunk is the chunk  were you can write and execute code while regular text is just used to write down comments.
6. You could use different types of graphs to visualize data, add text with explanations, results and other analysis.

